\documentclass[twoside,a4paper,10pt]{article}
\usepackage[top=2.54cm,bottom=2.54cm,left=2.54cm,right=2.54cm]{geometry}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{url}

\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{placeins}
%\usepackage{ref}

%%%

\pagenumbering{arabic}
\usepackage{fancyhdr}

\pagestyle{fancy}
% Shows section number and name
\renewcommand{\sectionmark}[1]{\markright{#1}{}}
% Clear previous styles
\fancyhf{}
\fancyhead{}
\fancyhead[RO]{\thepage}
\fancyhead[LO]{\rightmark}
\fancyhead[RE]{BitTorrent Tracker: deliverable 3}
\fancyhead[LE]{\thepage}
\fancyfoot{}
% Other modifiers
%\fancyfoot[LE,RO]{\thepage}
%\fancyfoot[LO,CE]{Something}
%\fancyfoot[CO,RE]{Author Name}

\title{BitTorrent Tracker: deliverable 3\\
  Group 01}
\author{Irene Díez \and Jesus Sesma}

\begin{document}
\date{}
\maketitle

%\begin{abstract}
%Your abstract.
%\end{abstract}
\section{Threads}\label{sec:pa-hierarchy}

Our application uses the following threads:
\begin{itemize}
\item \texttt{tracker.networking.runnables}: threads for networking purposes.
  \begin{enumerate}
  \item \texttt{NetworkerReadRunnable}: thread to read messages.
  \item \texttt{NetworkerWriteRunnable}: thread to write messages.
  \item \texttt{NetworkerPeerReadRunnable}: thread to read messages from the
    peer. Not used in this deliverable, but it has been left for completeness.
  \item \texttt{NetworkerPeerWriteRunnable}: thread to write messages from the
    peer. Not used in this deliverable, but it has been left for completeness.
  \item \texttt{NetworkerStatusRunnable}: thread to display a status image,
    used in our testing phase.
  \end{enumerate}
\item \texttt{tracker.subsys.cfts.FaultToleranceSys}: threads to handle
  the Fault Tolerance System.
  \begin{enumerate}
  \item \textbf{Main thread}: initialises the \texttt{FaultToleranceSys}'
    listeners.
  \item \textbf{KA timer thread}: to send KA messages.
  \item \textbf{HI timer thread}: to send HI messages.
  \end{enumerate}
\item \texttt{tracker.subsys.db.DBFaultToleranceSys}: threads to handle
  the Database Fault Tolerance System.
  \begin{enumerate}
  \item \textbf{Main thread}: handles if the master has to send an Announce
    or a Commit order again.
  \end{enumerate}
\item \texttt{tracker.subsys.election.MasterElectionSys}: threads to handle
  the MasterElectionSystem.
  \begin{enumerate}
  \item \textbf{Main thread}: initialises the  \texttt{MasterElectionSys}'
    listeners.
  \end{enumerate}
\end{itemize}

%\bibliographystyle{unsrt}
%\bibliography{bib}

\end{document}


